MLExplain

### 2018-05-23 paper.tex
Small tweaks
jsexplain bib entry
mlexplain architecture

%\documentclass{article}
\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}

@@

\begin{abstract}
	MLExplain is a step-by-step visual interpreter for OCaml that enables the user
	to inspect both their program's state and the interpreter's state itself. This interpreter
	aims to provide the user with a better understanding of OCaml's semantics.
\end{abstract}

@@

The semantics of a programming language can be very complex. When a language has no specification,
the semantics is then defined by the implementations of the language, i.e. interpreters and
compilers. However even when a specification is available, it can be difficult to understand why
the execution of a specific program results to a certain output.

The project \emph{JSExplain}\footnote{https://github.com/jscert/jsexplain} aims to describe
a JavaScript program's execution by showing every step of an interpreter which behavior is the
closest to JavaScript specification. This paper shows how we adapted JSExplain to OCaml.

@@

>>>>

%\documentclass{article}
\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usetikzlibrary{positioning,fit,shapes,arrows.meta}

@@

\begin{abstract}
	MLExplain is a step-by-step visual interpreter for OCaml that enables the user
	to inspect both their program's state and the interpreter's state itself. This interpreter
	aims to provide the user with a better understanding of the semantics of OCaml.
\end{abstract}

@@

The semantics of a programming language can be very complex. When a language has no specification,
the semantics is then defined by the implementations of the language, i.e., interpreters and
compilers. However even when a specification is available, it can be difficult to understand why
the execution of a specific program results to a certain output.

The project \emph{JSExplain} \cite{chargueraud:hal-01745792} aims to describe
a JavaScript program's execution by showing every step of an interpreter which behavior is the
closest to JavaScript specification. This paper shows how we adapted JSExplain to OCaml.

@@

\begin{figure*}
  \centering
  \begin{tikzpicture}[nodes = {align = center}]
    \node (focaml) [draw, text width=2cm] {Interpreter and libraries (OCaml)};

    \node (fjs) [draw, right = 1cm of focaml, text width=2cm, rectangle split,
    rectangle split parts=2, text centered] {Libraries (JS) \nodepart{second}
      Interpreter with traces (JS)};

    \node (ast) [draw, above = of fjs, text width=2cm] {AST of interpreted
      program};

    \node (source) [draw, right = 2cm of ast, text width=2cm, text centered]
    {interpreted program};

    \node [draw, dotted, fit=(fjs) (ast) (source)] {web page};

    \node (trace) [draw, right = 2cm of fjs, text width=2cm, text centered]
    {trace};

    \path[->,thick,>=stealth] (focaml.north
    east) edge[bend left] node[above left] {compiler} (fjs.north west) ;

    \path[->,thick,>=stealth] (focaml.south east) edge[bend right] node[below
    left] {\parbox{2cm}{\centering tracing compiler}} (fjs.south west);

    \path[->,thick,dotted,>=stealth] (source) edge node [above] {Parser} node [below] {Js\_of\_ocaml} (ast);

    \path[->,thick,dotted,>=stealth] (ast) edge (fjs);

    \path[->,thick,dotted,>=stealth] (ast) edge (fjs);

    \path[->,thick,dotted,>=stealth] (fjs) edge (trace);
  \end{tikzpicture}

  \caption{Architecture of MLExplain}
  \label{fig:archi}
\end{figure*}
